Discovery of s-process enhanced stars in the LAMOST survey

### 2018-09-21 article/ms.tex
abstract update

Here we present the discovery of 895 s-process candidates from 454,180 giant stars observed by LAMOST using a data-driven approach. This sample constitutes the largest number of s-process enhanced stars ever discovered. Our sample includes; 187 s-process candidates that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars that show only strontium enhancement. Most of our sample are within temperature and log g ranges consistent with RGB populations, this is consistent with our selection bias towards finding RGB stars. The majority of our s-process candidates ($95\%$) show strong carbon enhancements yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in tension with previous observations of enhanced Na among s-process candidates. We argue this may have been a systematic bias in previous studies. Our kinematical analysis reveals our sample is composed of 97\% disk stars, and 3\% with velocity consistent to the halo. A comparison with AGB yields suggests the main neutron source responsible for Ba and Sr enhancements is the $\text{C}^{13}$(\textrm{$\alpha$},n)$\text{O}^{16}$ reaction chain. Theoretical models show that this source is dominant in low-mass AGB stars. We conclude that the progenitors for s-process enhancement in our sample are AGB companion stars with masses $1 - 3\,M_{\odot}$.

>>>>

Here we present the discovery of 895 s-process candidates from 454,180 giant stars observed by LAMOST using a data-driven approach. This sample constitutes the largest number of s-process enhanced stars ever discovered. Our sample includes; 187 s-process candidates that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars that show only strontium enhancement. Most of our sample are within temperature and log g ranges typical of RGB populations, this is consistent with our selection bias towards finding RGB stars. The majority of our s-process candidates ($95\%$) show strong carbon enhancements yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in tension with previous observations of enhanced Na among s-process candidates. We argue this may have been a systematic bias in previous studies. Our kinematical analysis reveals our sample is composed of 97\% disk stars, and 3\% with velocity consistent to the halo. A comparison with AGB yields suggests the main neutron source responsible for Ba and Sr enhancements is the $\text{C}^{13}$(\textrm{$\alpha$},n)$\text{O}^{16}$ reaction chain. Theoretical models show that this source is dominant in low-mass AGB stars. We conclude that the progenitors for s-process enhancement in our sample are AGB companion stars with masses $1 - 3\,M_{\odot}$.
